DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life

### 2022-05-31 manuscript/manuscript.Rmd
fixing table 1 format and other edits

_**Searching the database.-**_
DateLife used the processed input names to search the local chronogram database and found 9 matching chronograms in 6 different studies (Fig. \ref{fig:figure2}B). Three studies matched five input names [@barker2015new; @Hedges2015; @Jetz2012], one study matched four input names [@hooper2017chromosomal] and two studies matched two input names [@barker2013going; @burns2014phylogenetics]. No studies matched all input names. Together, matching chronograms have 28 unique age data points. All nodes have age data.

_**Summarizing search results.-**_
DateLife obtained OpenTree's synthetic tree topology for these taxa (Fig. \ref{fig:figure2}C), and mapped age data to nodes in this chosen topology.
As expected, more inclusive nodes (e.g., node "n1") have more age data than less inclusive nodes (e.g., node "n5").
The name processing step allowed including five data points for node "n4" (parent of _Schoeniclus elegans_; Fig. \ref{fig:figure2}A) that would not have had any data otherwise due to name mismatch.
Age summary statistics per node were calculated and used as calibrations to date the tree topology using the BLADJ algorithm.
Age data for node "n2" was excluded as final calibration because it is older than age data of the more inclusive node "n1" (Fig. \ref{fig:figure2}C4).

>>>>

_**Searching the database.-**_
DateLife used the processed input names to search the local chronogram database and found 9 matching chronograms in 6 different studies (Fig. \ref{fig:figure2}B). Three studies matched five input names [@barker2015new; @Hedges2015; @Jetz2012], one study matched four input names [@hooper2017chromosomal] and two studies matched two input names [@barker2013going; @burns2014phylogenetics]. No studies matched all input names. Together, source chronograms provide 28 unique age data points, covering all nodes on our chosen tree topology to date (Table \ref{tbl:table1}).

_**Summarizing search results.-**_
DateLife obtained OpenTree's synthetic tree topology for these taxa (Fig. \ref{fig:figure2}C), and mapped age data to nodes in this chosen topology.
As expected, more inclusive nodes (e.g., node "n1") have more variance in age data than less inclusive nodes (e.g., node "n5").
The name processing step allowed including five data points for node "n4" (parent of _Schoeniclus elegans_; Fig. \ref{fig:figure2}A) that would not have had any data otherwise due to name mismatch.
Age summary statistics per node were calculated and used as calibrations to date the tree topology using the BLADJ algorithm.
Age data for node "n2" was excluded as final calibration because it is older than age data of the more inclusive node "n1" (Fig. \ref{fig:figure2}C4).

### 2022-05-31 manuscript/manuscript.tex
creating table 1 as .tex in small example vignette, and adding it to manuscript as graphic
fixing table 1 format and other edits

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Tree; Phylogeny; Scaling; Dating; Ages; Divergence times; Open Science; Congruification; Supertree; Calibrations; Secondary calibrations\newline\indent Word count: 4823}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

\emph{\textbf{Searching the database.-}}
DateLife used the processed input names to search the local chronogram database and found 9 matching chronograms in 6 different studies (Fig. \ref{fig:figure2}B). Three studies matched five input names (Barker, Burns, Klicka, Lanyon, \& Lovette, 2015; Hedges, Marin, Suleski, Paymer, \& Kumar, 2015; Jetz, Thomas, Joy, Hartmann, \& Mooers, 2012), one study matched four input names (Hooper \& Price, 2017) and two studies matched two input names (Barker, Burns, Klicka, Lanyon, \& Lovette, 2013; Burns et al., 2014). No studies matched all input names. Together, matching chronograms have 28 unique age data points. All nodes have age data.

\emph{\textbf{Summarizing search results.-}}
DateLife obtained OpenTree's synthetic tree topology for these taxa (Fig. \ref{fig:figure2}C), and mapped age data to nodes in this chosen topology.
As expected, more inclusive nodes (e.g., node ``n1'') have more age data than less inclusive nodes (e.g., node ``n5'').
The name processing step allowed including five data points for node ``n4'' (parent of \emph{Schoeniclus elegans}; Fig. \ref{fig:figure2}A) that would not have had any data otherwise due to name mismatch.
Age summary statistics per node were calculated and used as calibrations to date the tree topology using the BLADJ algorithm.
Age data for node ``n2'' was excluded as final calibration because it is older than age data of the more inclusive node ``n1'' (Fig. \ref{fig:figure2}C4).

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%    FIGURE 3    %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\includegraphics{../figures/fringillidae-topologies/fringillidae-topology.pdf}
\caption{Tree topologies obtained from Open Tree of Life's (OpenTree) synthetic phylogenetic tree. A) Topology of 2,333 tips and 1,305 internal nodes, encompassing bird species within the family Fringillidae following the NCBI taxonomy (black), as well as all other bird species that share the same mrca node in OpenTree's synthetic tree (purple). B) Topology of 289 tips and 253 internal nodes, encompassing bird species within the Fringillidae only, resulting from pruning purple branches from topology A.
Bird species within the Fringillidae do not form a monophyletic group
(Alström et al. \protect\hyperlink{ref-}{2014},
Barker, Cibois, Schikler, Feinstein, \& Cracraft \protect\hyperlink{ref-barker2004phylogeny}{2004},
Barker et al. \protect\hyperlink{ref-barker2013going}{2013},
Barker \protect\hyperlink{ref-barker2014mitogenomic}{2014},
Barker et al. \protect\hyperlink{ref-barker2015new}{2015},
Beresford, Barker, Ryan, \& Crowe \protect\hyperlink{ref-beresford2005african}{2005},
Bryson Jr et al. \protect\hyperlink{ref-bryson2014diversification}{2014},
Burleigh, Kimball, \& Braun \protect\hyperlink{ref-burleigh2015building}{2015},
Burns et al. \protect\hyperlink{ref-burns2014phylogenetics}{2014},
Chaves, Hidalgo, \& Klicka \protect\hyperlink{ref-chaves2013biogeography}{2013},
Claramunt \& Cracraft \protect\hyperlink{ref-claramunt2015new}{2015},
Gibb et al. \protect\hyperlink{ref-gibb2015new}{2015},
Hackett et al. \protect\hyperlink{ref-hackett2008phylogenomic}{2008},
Jetz et al. \protect\hyperlink{ref-Jetz2012}{2012},
Johansson, Fjeldså, \& Bowi \protect\hyperlink{ref-johansson2008phylogenetic}{200},
Kimball et al. \protect\hyperlink{ref-kimball2019phylogenomic}{2019},
Klicka et al. \protect\hyperlink{ref-klicka2014comprehensive}{2014},
Lamichhaney et al. \protect\hyperlink{ref-lamichhaney2015evolution}{2015},
Lerner, Meyer, James, Hofreiter, \& Fleischer \protect\hyperlink{ref-lerner2011multilocus}{2011},
Lovette et al. \protect\hyperlink{ref-lovette2010comprehensive}{2010},
Moyle et al. \protect\hyperlink{ref-moyle2016tectonic}{2016},
Ödeen, Håstad, \& Alström \protect\hyperlink{ref-odeen2011evolution}{2011},
Oliveros et al. \protect\hyperlink{ref-oliveros2019earth}{2019},
Päckert et al. \protect\hyperlink{ref-packert2012horizontal}{2012},
Parchman, Benkman, \& Mezquida \protect\hyperlink{ref-parchman2007coevolution}{2007},
Powell et al. \protect\hyperlink{ref-powell2014comprehensive}{2014},
Price et al. \protect\hyperlink{ref-price2014niche}{2014},
Pulgarín-R, Smith, Bryson Jr, Spellman, \& Klicka \protect\hyperlink{ref-pulgarin2013multilocus}{2013},
Selvatti, Gonzaga, \& Moraes Russo \protect\hyperlink{ref-selvatti2015paleogene}{2015},
Tietze, Päckert, Martens, Lehmann, \& Sun \protect\hyperlink{ref-tietze2013complete}{2013},
Treplin et al. \protect\hyperlink{ref-treplin2008molecular}{2008},
Zuccon, Prŷs-Jones, Rasmussen, \& Ericson \protect\hyperlink{ref-zuccon2012phylogenetic}{2012}).
}
\label{fig:fringillidae-topologies}
\end{figure}

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Tree; Phylogeny; Scaling; Dating; Ages; Divergence times; Open Science; Congruification; Supertree; Calibrations; Secondary calibrations\newline\indent Word count: 4834}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

\emph{\textbf{Searching the database.-}}
DateLife used the processed input names to search the local chronogram database and found 9 matching chronograms in 6 different studies (Fig. \ref{fig:figure2}B). Three studies matched five input names (Barker, Burns, Klicka, Lanyon, \& Lovette, 2015; Hedges, Marin, Suleski, Paymer, \& Kumar, 2015; Jetz, Thomas, Joy, Hartmann, \& Mooers, 2012), one study matched four input names (Hooper \& Price, 2017) and two studies matched two input names (Barker, Burns, Klicka, Lanyon, \& Lovette, 2013; Burns et al., 2014). No studies matched all input names. Together, source chronograms provide 28 unique age data points, covering all nodes on our chosen tree topology to date (Table \ref{tbl:table1}).

\emph{\textbf{Summarizing search results.-}}
DateLife obtained OpenTree's synthetic tree topology for these taxa (Fig. \ref{fig:figure2}C), and mapped age data to nodes in this chosen topology.
As expected, more inclusive nodes (e.g., node ``n1'') have more variance in age data than less inclusive nodes (e.g., node ``n5'').
The name processing step allowed including five data points for node ``n4'' (parent of \emph{Schoeniclus elegans}; Fig. \ref{fig:figure2}A) that would not have had any data otherwise due to name mismatch.
Age summary statistics per node were calculated and used as calibrations to date the tree topology using the BLADJ algorithm.
Age data for node ``n2'' was excluded as final calibration because it is older than age data of the more inclusive node ``n1'' (Fig. \ref{fig:figure2}C4).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%    TABLE 1     %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \caption{Ages of congruified nodes belonging to step C3 from Figure3}
  \label{tbl:table1}
  \includegraphics[width=\linewidth]{../tables/table-fringillidae-small-example.pdf}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%    FIGURE 3    %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\includegraphics{../figures/fringillidae-topologies/fringillidae-topology.pdf}
\caption{Tree topologies obtained from Open Tree of Life's (OpenTree) synthetic phylogenetic tree.
A) Topology of 2,333 tips and 1,305 internal nodes, encompassing bird species within the family Fringillidae following the NCBI taxonomy (black), as well as all other bird species that share the same mrca node in OpenTree's synthetic tree (purple).
B) Topology of 289 tips and 253 internal nodes, encompassing bird species within the Fringillidae only.
This tree results from pruning species that are not assigned to the family Fringillidae (purple branches in topology A) but that form a monophyletic group with them.
Bird species within the Fringillidae are paraphyletic
(Alström et al. \protect\hyperlink{ref-}{2014},
Barker, Cibois, Schikler, Feinstein, \& Cracraft \protect\hyperlink{ref-barker2004phylogeny}{2004},
Barker et al. \protect\hyperlink{ref-barker2013going}{2013},
Barker \protect\hyperlink{ref-barker2014mitogenomic}{2014},
Barker et al. \protect\hyperlink{ref-barker2015new}{2015},
Beresford, Barker, Ryan, \& Crowe \protect\hyperlink{ref-beresford2005african}{2005},
Bryson Jr et al. \protect\hyperlink{ref-bryson2014diversification}{2014},
Burleigh, Kimball, \& Braun \protect\hyperlink{ref-burleigh2015building}{2015},
Burns et al. \protect\hyperlink{ref-burns2014phylogenetics}{2014},
Chaves, Hidalgo, \& Klicka \protect\hyperlink{ref-chaves2013biogeography}{2013},
Claramunt \& Cracraft \protect\hyperlink{ref-claramunt2015new}{2015},
Gibb et al. \protect\hyperlink{ref-gibb2015new}{2015},
Hackett et al. \protect\hyperlink{ref-hackett2008phylogenomic}{2008},
Jetz et al. \protect\hyperlink{ref-Jetz2012}{2012},
Johansson, Fjeldså, \& Bowi \protect\hyperlink{ref-johansson2008phylogenetic}{200},
Kimball et al. \protect\hyperlink{ref-kimball2019phylogenomic}{2019},
Klicka et al. \protect\hyperlink{ref-klicka2014comprehensive}{2014},
Lamichhaney et al. \protect\hyperlink{ref-lamichhaney2015evolution}{2015},
Lerner, Meyer, James, Hofreiter, \& Fleischer \protect\hyperlink{ref-lerner2011multilocus}{2011},
Lovette et al. \protect\hyperlink{ref-lovette2010comprehensive}{2010},
Moyle et al. \protect\hyperlink{ref-moyle2016tectonic}{2016},
Ödeen, Håstad, \& Alström \protect\hyperlink{ref-odeen2011evolution}{2011},
Oliveros et al. \protect\hyperlink{ref-oliveros2019earth}{2019},
Päckert et al. \protect\hyperlink{ref-packert2012horizontal}{2012},
Parchman, Benkman, \& Mezquida \protect\hyperlink{ref-parchman2007coevolution}{2007},
Powell et al. \protect\hyperlink{ref-powell2014comprehensive}{2014},
Price et al. \protect\hyperlink{ref-price2014niche}{2014},
Pulgarín-R, Smith, Bryson Jr, Spellman, \& Klicka \protect\hyperlink{ref-pulgarin2013multilocus}{2013},
Selvatti, Gonzaga, \& Moraes Russo \protect\hyperlink{ref-selvatti2015paleogene}{2015},
Tietze, Päckert, Martens, Lehmann, \& Sun \protect\hyperlink{ref-tietze2013complete}{2013},
Treplin et al. \protect\hyperlink{ref-treplin2008molecular}{2008},
Zuccon, Prŷs-Jones, Rasmussen, \& Ericson \protect\hyperlink{ref-zuccon2012phylogenetic}{2012}).
}
\label{fig:fringillidae-topologies}
\end{figure}

### 2022-05-31 manuscript/table-fringillidae-small-example.tex
fixing table 1 format and other edits

\caption{\label{tab:table1}Table 1. Ages of congruified nodes.}
\centering
\begin{tabular}[t]{l|c|c|c|c|c}
\hline
  & Node Name & taxon A & taxon B & Node Age & Study chronogram\\
\hline
1 & n1 & Emberiza citrinella & Platyspiza crassirostris & 9.6509881 & Jetz, W., G. H. Thomas, J. B. Joy, K. Hartmann, A. O. Mooers. 2012. The global diversity of birds in space and time. Nature 491 (7424): 444-448\\
\hline
2 & n1 & Pheucticus tibialis & Schoeniclus elegans & 14.3336520 & Barker, F. Keith, Kevin J. Burns, John Klicka, Scott M. Lanyon, Irby J. Lovette. 2015. New insights into New World biogeography: An integrated view from the phylogeny of blackbirds, cardinals, sparrows, tanagers, warblers, and allies. The Auk 132 (2): 333-348.\\
\hline
3 & n1 & Rhodothraupis celaeno & Schoeniclus elegans & 16.2984859 & Barker, F. Keith, Kevin J. Burns, John Klicka, Scott M. Lanyon, Irby J. Lovette. 2015. New insights into New World biogeography: An integrated view from the phylogeny of blackbirds, cardinals, sparrows, tanagers, warblers, and allies. The Auk 132 (2): 333-348.\\
\hline
4 & n1 & Emberiza citrinella & Platyspiza crassirostris & 16.9499615 & Hooper, Daniel M., Trevor D. Price. 2017. Chromosomal inversion differences correlate with range overlap in passerine birds. Nature Ecology \& Evolution 1 (10): 1526-1534\\
\hline
5 & n1 & Rhodothraupis celaeno & Schoeniclus elegans & 21.5140867 & Jetz, W., G. H. Thomas, J. B. Joy, K. Hartmann, A. O. Mooers. 2012. The global diversity of birds in space and time. Nature 491 (7424): 444-448\\
\hline
6 & n1 & Emberiza leucocephalos & Platyspiza crassirostris & 22.0000000 & Hedges, S. Blair, Julie Marin, Michael Suleski, Madeline Paymer, Sudhir Kumar. 2015. Tree of life reveals clock-like speciation and diversification. Molecular Biology and Evolution 32 (4): 835-845\\
\hline
7 & n1 & Emberiza citrinella & Platyspiza crassirostris & 22.3757277 & Hedges, S. Blair, Julie Marin, Michael Suleski, Madeline Paymer, Sudhir Kumar. 2015. Tree of life reveals clock-like speciation and diversification. Molecular Biology and Evolution 32 (4): 835-845\\
\hline
8 & n2 & Platyspiza crassirostris & Rhodothraupis celaeno & 7.9691925 & Jetz, W., G. H. Thomas, J. B. Joy, K. Hartmann, A. O. Mooers. 2012. The global diversity of birds in space and time. Nature 491 (7424): 444-448\\
\hline
9 & n2 & Platyspiza crassirostris & Rhodothraupis celaeno & 19.7085900 & Hedges, S. Blair, Julie Marin, Michael Suleski, Madeline Paymer, Sudhir Kumar. 2015. Tree of life reveals clock-like speciation and diversification. Molecular Biology and Evolution 32 (4): 835-845\\
\hline
10 & n2 & Pheucticus tibialis & Platyspiza crassirostris & 44.2958603 & Burns, Kevin J., Allison J. Shultz, Pascal O. Title, Nicholas A. Mason, F. Keith Barker, John Klicka, Scott M. Lanyon, Irby J. Lovette. 2014. Phylogenetics and diversification of tanagers (Passeriformes: Thraupidae), the largest radiation of Neotropical songbirds. Molecular Phylogenetics and Evolution 75: 41-77.\\
\hline
11 & n3 & Pheucticus tibialis & Rhodothraupis celaeno & 10.5304440 & Barker, F. Keith, Kevin J. Burns, John Klicka, Scott M. Lanyon, Irby J. Lovette. 2015. New insights into New World biogeography: An integrated view from the phylogeny of blackbirds, cardinals, sparrows, tanagers, warblers, and allies. The Auk 132 (2): 333-348.\\
\hline
12 & n3 & Pheucticus tibialis & Rhodothraupis celaeno & 10.5379092 & Barker, F. K., K. J. Burns, J. Klicka, S. M. Lanyon, I. J. Lovette. 2013. Going to extremes: contrasting rates of diversification in a recent radiation of New World passerine birds. Systematic Biology 62 (2): 298-320.\\
\hline
13 & n3 & Pheucticus tibialis & Rhodothraupis celaeno & 18.1570685 & Hedges, S. Blair, Julie Marin, Michael Suleski, Madeline Paymer, Sudhir Kumar. 2015. Tree of life reveals clock-like speciation and diversification. Molecular Biology and Evolution 32 (4): 835-845\\
\hline
14 & n4 & Emberiza citrinella & Schoeniclus elegans & 5.3238969 & Jetz, W., G. H. Thomas, J. B. Joy, K. Hartmann, A. O. Mooers. 2012. The global diversity of birds in space and time. Nature 491 (7424): 444-448\\
\hline
15 & n4 & Emberiza leucocephalos & Schoeniclus elegans & 9.8622460 & Barker, F. Keith, Kevin J. Burns, John Klicka, Scott M. Lanyon, Irby J. Lovette. 2015. New insights into New World biogeography: An integrated view from the phylogeny of blackbirds, cardinals, sparrows, tanagers, warblers, and allies. The Auk 132 (2): 333-348.\\
\hline
16 & n4 & Emberiza leucocephalos & Schoeniclus elegans & 10.3391445 & Jetz, W., G. H. Thomas, J. B. Joy, K. Hartmann, A. O. Mooers. 2012. The global diversity of birds in space and time. Nature 491 (7424): 444-448\\
\hline
17 & n4 & Emberiza citrinella & Schoeniclus elegans & 12.5133870 & Hooper, Daniel M., Trevor D. Price. 2017. Chromosomal inversion differences correlate with range overlap in passerine birds. Nature Ecology \& Evolution 1 (10): 1526-1534\\
\hline
18 & n5 & Emberiza citrinella & Emberiza leucocephalos & 0.1407015 & Jetz, W., G. H. Thomas, J. B. Joy, K. Hartmann, A. O. Mooers. 2012. The global diversity of birds in space and time. Nature 491 (7424): 444-448\\
\hline
19 & n5 & Emberiza citrinella & Emberiza leucocephalos & 0.1516230 & Hedges, S. Blair, Julie Marin, Michael Suleski, Madeline Paymer, Sudhir Kumar. 2015. Tree of life reveals clock-like speciation and diversification. Molecular Biology and Evolution 32 (4): 835-845\\
\hline
20 & n5 & Emberiza citrinella & Emberiza leucocephalos & 0.2011990 & Barker, F. Keith, Kevin J. Burns, John Klicka, Scott M. Lanyon, Irby J. Lovette. 2015. New insights into New World biogeography: An integrated view from the phylogeny of blackbirds, cardinals, sparrows, tanagers, warblers, and allies. The Auk 132 (2): 333-348.\\
\hline
21 & n5 & Emberiza citrinella & Emberiza leucocephalos & 2.2898230 & Hooper, Daniel M., Trevor D. Price. 2017. Chromosomal inversion differences correlate with range overlap in passerine birds. Nature Ecology \& Evolution 1 (10): 1526-1534\\
\hline
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:table1}Ages of congruified nodes.}
\centering
\begin{tabular}[t]{l|c|c|c|c|c}
\hline
  & Node Name & taxon A & taxon B & Node Age & Study chronogram\\
\hline
1 & n1 & Emberiza citrinella & Platyspiza crassirostris & 9.6509881 & Jetz et al. 2012 - chronogram 1\\
\hline
2 & n1 & Pheucticus tibialis & Schoeniclus elegans & 14.3336520 & Barker et al. 2015 - chronogram 1\\
\hline
3 & n1 & Rhodothraupis celaeno & Schoeniclus elegans & 16.2984859 & Barker et al. 2015 - chronogram 2\\
\hline
4 & n1 & Emberiza citrinella & Platyspiza crassirostris & 16.9499615 & Hooper et al. 2017\\
\hline
5 & n1 & Rhodothraupis celaeno & Schoeniclus elegans & 21.5140867 & Jetz et al. 2012 - chronogram 2\\
\hline
6 & n1 & Emberiza leucocephalos & Platyspiza crassirostris & 22.0000000 & Hedges et al. 2015 - chronogram 2\\
\hline
7 & n1 & Emberiza citrinella & Platyspiza crassirostris & 22.3757277 & Hedges et al. 2015 - chronogram 1\\
\hline
8 & n2 & Platyspiza crassirostris & Rhodothraupis celaeno & 7.9691925 & Jetz et al. 2012 - chronogram 1\\
\hline
9 & n2 & Platyspiza crassirostris & Rhodothraupis celaeno & 19.7085830 & Jetz et al. 2012 - chronogram 2\\
\hline
10 & n2 & Platyspiza crassirostris & Rhodothraupis celaeno & 19.7085900 & Hedges et al. 2015 - chronogram 2\\
\hline
11 & n2 & Platyspiza crassirostris & Rhodothraupis celaeno & 19.7128363 & Hedges et al. 2015 - chronogram 1\\
\hline
12 & n2 & Pheucticus tibialis & Platyspiza crassirostris & 44.2958603 & Burns et al. 2014\\
\hline
13 & n3 & Pheucticus tibialis & Rhodothraupis celaeno & 10.5304440 & Barker et al. 2015 - chronogram 1\\
\hline
14 & n3 & Pheucticus tibialis & Rhodothraupis celaeno & 10.5379092 & Barker et al. 2013\\
\hline
15 & n3 & Pheucticus tibialis & Rhodothraupis celaeno & 11.2095375 & Barker et al. 2015 - chronogram 2\\
\hline
16 & n3 & Pheucticus tibialis & Rhodothraupis celaeno & 18.1570685 & Hedges et al. 2015 - chronogram 1\\
\hline
17 & n4 & Emberiza citrinella & Schoeniclus elegans & 5.3238969 & Jetz et al. 2012 - chronogram 1\\
\hline
18 & n4 & Emberiza leucocephalos & Schoeniclus elegans & 9.8622460 & Barker et al. 2015 - chronogram 1\\
\hline
19 & n4 & Emberiza leucocephalos & Schoeniclus elegans & 10.3391445 & Jetz et al. 2012 - chronogram 2\\
\hline
20 & n4 & Emberiza leucocephalos & Schoeniclus elegans & 11.7317630 & Barker et al. 2015 - chronogram 2\\
\hline
21 & n4 & Emberiza citrinella & Schoeniclus elegans & 12.5133870 & Hooper et al. 2017\\
\hline
22 & n5 & Emberiza citrinella & Emberiza leucocephalos & 0.1407015 & Jetz et al. 2012 - chronogram 1\\
\hline
23 & n5 & Emberiza citrinella & Emberiza leucocephalos & 0.1516230 & Hedges et al. 2015 - chronogram 2\\
\hline
24 & n5 & Emberiza citrinella & Emberiza leucocephalos & 0.2011990 & Barker et al. 2015 - chronogram 1\\
\hline
25 & n5 & Emberiza citrinella & Emberiza leucocephalos & 0.2409300 & Barker et al. 2015 - chronogram 2\\
\hline
26 & n5 & Emberiza citrinella & Emberiza leucocephalos & 0.2732460 & Jetz et al. 2012 - chronogram 2\\
\hline
27 & n5 & Emberiza citrinella & Emberiza leucocephalos & 0.5760260 & Hedges et al. 2015 - chronogram 1\\
\hline
28 & n5 & Emberiza citrinella & Emberiza leucocephalos & 2.2898230 & Hooper et al. 2017\\
\hline
\end{tabular}
\end{table}
